|

### 2025-10-20 manuscript/manuscript_preprint.qmd
tried installing aft but deleted - will sort later

---
title: "Methods and Results"
format: docx
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)

>>>>

---
title: |
  Does resting energy expenditure differ between women with and without polycystic ovary syndrome (PCOS): a systematic review and meta-analysis
format:
  pdf: default
  aft-pdf:
    keep-tex: true
author:
  - name: James Steele
    affiliations:
      - ref: 1
      - ref: 2
      - ref: 3
    orcid: 0000-0002-8003-0757
    corresponding: true
    email: james@steele-research.com
  - name: James Fisher
    affiliations:
      - ref: 3
      - ref: 4
    orcid: 0000-0002-6013-8402
    email: james.fisher.phd@outlook.com
  - name: Tim Dettmann
    affiliations:
      - ref: 1
    email: tim.dettmann@gmail.com
affiliations:
      - id: 1
        name: Kieser Australia, Melbourne, Australia
      - id: 2
        name: Steele Research Limited, Eastleigh, UK
      - id: 3
        name: Department of Sport and Health, Solent University, Southampton, UK
      - id: 4
        name: The Exercise Coach, Tennessee, USA
abstract: |
  To write
pdf-engine: xelatex
bibliography: 
  mylibrary.bib
csl: apa.csl
execute: 
  echo: false
  message: false
  warning: false
---
```{r}
library(tidyverse)
library(flextable)
library(tidybayes)
